Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-18 article.tex
feynman words 40 yrs ago

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
Richard Feynman’s words are as true today as when he spoke them: “Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful problem, because it doesn't look so easy.”

>>>>

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
Richard Feynman’s words are as true today as when he spoke them almost forty years ago: “Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful problem, because it doesn't look so easy.”
